Higher-Order unification for free!

### 2024-04-10 paper/main.tex
explain diamond

\subsection{The solution (in a nutshell)}
\label{sec:nutshell}
A term $s$ is compiled to a term $t$ where every
``problematic'' sub term $p$ is replaced by a fresh unification variable $h$
with an accessory \emph{link} that represents a suspended unification problem
$h \Ue p$. As a result \Ue is ``well behaved'' on $t$, in the sense that
it does not contradict \Eo as it would otherwise do on the
``problematic'' sub-terms.\\
We now define ``problematic'' and ``well behaved'' more formally.

@@

% \noteD{Paragraph for decompile in case of \maybebeta}
Decompilation of \linkbeta is possible by extending \elpiIn{commit-link} with
new heuristics.

>>>>

\subsection{The solution (in a nutshell)}
\label{sec:nutshell}
A term $s$ is compiled to a term $t$ where every
``problematic'' sub term $p$ is replaced by a fresh unification variable $h$
with an accessory \emph{link} that represents a suspended unification problem
$h \Ue p$. As a result \Ue is ``well behaved'' on $t$, in the sense that
it does not contradict \Eo as it would otherwise do on the
``problematic'' sub-terms.\\
We now define ``problematic'' and ``well behaved'' more formally
and we pick the $\Diamond$ symbol since it
stands for ``possibly'' in modal logic and all problematic terms
are characterized by some ``uncertainty''.

@@

% \noteD{Paragraph for decompile in case of \maybebeta}
Decompilation of \linkbeta is possible by extending \elpiIn{commit-link} with
new heuristics.
\todo{cita paper su estensioni a llam via sospensione etc}
\todo{cita teyjus (1) era 2nd order HO (huet's algorithm), teyjus 2 è llam ma sospende i disagreement pairs fuori da llam}
